---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Stressing Dynamic Loss Models

<!-- badges: start -->
<!-- badges: end -->

This code implements the algorithms described in our paper "Stressing Dynamic Loss Models" (Kroell, Pesenti, and Jaimungal, 2022). This is joint work with Silvana M. Pesenti and Sebastian Jaimungal.

## Example

Below we provide a few examples of working with our code to stress dynamic loss models, as described by compound Poisson processes.

```{r example, echo = FALSE}
library(revpathsensitivity)
```

In this example, we set the jump size distribution to $\Gamma(\alpha, \beta)$ where $\alpha = 2$ and $\beta = 1$. We first create a class containing all the information needed on this random variable.

```{r}
# jump size is Gamma(2,1) distributed
# Set up distribution class
gamma_2_1 <- RPS_dist_univ(dist_fun = function(x,parms) pgamma(x,shape=parms$alpha,
                                                               rate=parms$beta),
                           dens_fun = function(x,parms) dgamma(x,shape=parms$alpha,
                                                               rate=parms$beta),
                           sim_fun = function(x,parms) rgamma(x,shape=parms$alpha,
                                                              rate=parms$beta),
                           char_fun = function(x,parms) (1 - 1i*x/parms$beta)^(-parms$alpha),
                           min = 0,
                           max = qgamma(1-1e-10,shape=2,rate=1),
                           mean_fun = function(parms) parms$alpha/parms$beta,
                           parms = list(alpha = 2, beta=1))
```

We decide to stress the 90\% VaR of the model up 10\%. This code imposes the stress and simulates under the model.

```{r}
ex_gamma_VaR <- stressed_sim(kappa = 5, jump_dist = gamma_2_1, 
                             stress_type = "VaR",
                             stress_parms = list(c=0.9,VaR_stress=1.1),
                             Npaths=1e4, end_time=1, dt=2e-3)
```

Here we plot the output of the stressed model. We compare the paths under the stressed model to those under the baseline model, as well as to how the intensity of the jumps have changed under the stressed probability measure.

```{r}
plot_paths(ex_gamma_VaR, Npaths=15, quantiles=list(lower=0.1,upper=0.9))
```


### CVaR constraint

Now we want to impose an additional constraint, corresponding to an 8\% increase in CVaR (also known as Expected Shortfall).

```{r}
ex_gamma_CVaR <- stressed_sim(kappa = 5, jump_dist = gamma_2_1,
                              stress_type = "CVaR", 
                              stress_parms = list(c=0.9,
                                                 VaR_stress=1.1,
                                                 CVaR_stress=1.08),
                              Npaths=1e4, end_time=1, dt=2e-3)
```

Here we plot the paths of the stressed model as well as the jump intensity over time. 

```{r}
plot_paths(ex_gamma_CVaR, Npaths=15, quantiles=list(lower=0.1,upper=0.9))
```


### Bivariate example

We can also examine the case where $X_t$ is bivariate and a stress is applied to only the first component, $X^1_t$. In this example, we set the severity distributions to both be $\Gamma(2,1)$ with a dependence relationship given by the $t$-copula with correlation 0.8 and 3 degrees of freedom. The implementation of a $t$-copula with fixed marginals is done using the `copula` package.

```{r}
gamma_t <- RPS_dist_biv(copula=copula::tCopula(0.8,df=3,dim=2),
                        margins=c("gamma", "gamma"),
                        sim_fun = function(x,parms) rgamma(x,shape=parms$alpha1,
                                                           rate=parms$beta1),
                        dens_fun = function(x,parms) dgamma(x,shape=parms$alpha1,
                                                            rate=parms$beta1),
                        char_fun = function(x,parms) (1 - 1i*x/parms$beta1)^
                              (-parms$alpha1),
                          mean_fun = function(parms) parms$alpha1/parms$beta1,
                          parms = list(alpha1 = 2, beta1=1, alpha2=2, beta2=1))
```

Here we examine the effect of a 10\% increase in $\text{VaR}_{0.9}(X^1_T)$ at the 90\% level. 

```{r}
gamma_t_ex <- stressed_sim_biv(kappa = 5, jump_dist = gamma_t,
                               stress_type = "VaR",
                               stress_parms = list(c=0.9,VaR_stress=1.1),
                               Npaths=1e4, end_time=1, dt=2e-3)

```

```{r}
plot_paths_biv(gamma_t_ex, Npaths=15, quantiles=list(lower=0.1,upper=0.9))
```


We can also plot the contours of the copula density under $\mathbb{P}$ and $\mathbb{Q}$. Here we plot it at the terminal time, $t=1$:

```{r}
plot_copula_dens_contour(gamma_t_ex,time=1)
```

## Installation

You can install the development version of revpathsensitivity from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("emmakroell/stressing-dynamic-loss-models")

# load code
library(revpathsensitivity)
```


