---
title: "gamma-jumps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gamma-jumps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(revpathsensitivity)
devtools::load_all()
```

In this example, we set the jump size distribution to $\Gamma(\alpha, \beta)$ where $\alpha = 2$ and $\beta = 1$. We first create a class containing all the information needed on this random variable.

```{r}
# jump size is Gamma(2,1) distributed
# Set up distribution class
gamma_2_1 <- new_RPS_dist(dist_fun = function(x,parms) pgamma(x,shape=parms$alpha,
                                                              rate=parms$beta),
                          dens_fun = function(x,parms) dgamma(x,shape=parms$alpha,
                                                              rate=parms$beta),
                          sim_fun = function(x,parms) rgamma(x,shape=parms$alpha,
                                                             rate=parms$beta),
                          char_fun = function(x,parms) (1 - 1i*x/parms$beta)^(-parms$alpha),
                          mean_fun = function(parms) parms$alpha/parms$beta,
                          parms = list(alpha = 2, beta=1)) 
```

We decide to stress the 90\% VaR of the model down about 20\%. this code imposes the stress and simulates under the model.

```{r}
# simulate
gamma_2_1_example <- stressed_sim(kappa = 5, jump_dist = gamma_2_1, 
                                  stress_type = "VaR",
                                  stress_parms = list(c=0.9,VaR_stress=0.8),
                                  Npaths=1e4, endtime=1, dt=1e-2)
```

Here we plot the output of the stressed model.

```{r}
path_plot(gamma_2_1_example, Npaths=20, quantiles=list(lower=0.1,upper=0.9))
```

We can also compare the paths under the stressed model to those under the baseline model.

```{r}
path_plot(gamma_2_1_example,
          Npaths = 20,
          quantiles=list(lower=0.1,upper=0.9),
          plot_type = "compare_to_baseline")
```

Finally, we can examine how the intensity of the jumps have changed under the stressed probability measure.

```{r}
path_plot(gamma_2_1_example,
          Npaths = 10,
          plot_type = "compare_to_kappa")
```

